\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[dvipdfmx]{hyperref}
\usepackage{pxjahyper}

\title{Waffle user's manual}
\author{Shunki Takami}

\begin{document}
\maketitle
\thispagestyle{empty}
\begin{table}[]
\begin{tabular}{ll}
2021-03-31 & Create \\
\end{tabular}
\end{table}

\newpage \thispagestyle{empty}
\tableofcontents
\newpage \setcounter{page}{1}

\section{Introduction}

\section{Overview}
Waffle is composed of global configurations, projects descriptions, and a task manager.


\section{Global configurations}
There are a system configuration and computers configuration.
\subsection{System configuration}
Currently, Waffle has not this configuration.

\subsection{Computers configuration}
You should list computers that is hosted calculation on this configuration.
The contents of configuration is a name,
a location of working directory on the computer,
a location of xsub,
a submitter type, and special configuration of the submitter.

Xsub

A submitter has a role for management tasks, 
and a computer is related to a submitter.
Waffle has multiple submitter types to support various types task management.

\subsection{Submitter type}

\section{Projects descriptions}
A project is composed of executables, conductors, and workspaces.

\subsection{Executable}
\subsection{Conductor}
\subsection{Workspace}

\section{Step by step tutorial}

\section{License}
Waffle is released under the BSD 3-Clause license.
The contained libraries license descriptions are displayed in System configuration page on the graphical user interface.

\end{document}

